---
title: "SWAT Output Post-Processing (Part 2)"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Overview

In post-processing part 1, we were introduced to the different SWAT output files, learned about tidy data concepts, and started importing SWAT outputs into R/RStudio. Here we will learn how to plot these data in ways that are helpful to our research.

By the end of this workshop session you will be able to:

1. *describe* common figures for exploring and publishing SWAT results

2. *modify* R code to import and plot SWAT data


## 2. Importing Data

First set your working directory as we did in post-processing part 1.

```{r set path, eval = FALSE, echo = TRUE}

setwd('/Users/ssaia/Documents/GitHub/ecohydro-modeling-workshop-mar2018/data/swat_output_data')
# copy/paste the path to the data directory inside the function setwd()
# windows users may have to change /'s to \\'s when copy/pasting

```

Next let's load our package.

```{r loading packages, results=FALSE, message = FALSE, warning=FALSE}

library(tidyverse) # do this each time you open a new script and need it

```

Now let's import the raw `output.rch` file. Note the extra funciton options we're including here: 

```{r import raw data, results = FALSE, echo = TRUE, message = FALSE, warning=FALSE}

# You will need to change what's between the 's here. It should be output.rch.
rch_data_raw = read_table2('/Users/ssaia/Documents/GitHub/ecohydro-modeling-workshop-mar2018/data/swat_output_data/output.rch', col_names=FALSE, skip=9)

```

Let's look at the data? What's different about it from the first time we tried importing it?

``` {r show raw data}

head(rch_data_raw, n = 20)

```

Ok, let's reformat these raw data a little more using the `reformat_monthly_rch_file()` function.

```{r reformat raw data}

source('reformat_monthly_rch_file.R') # add the reformat_rch_file() function to our working environment

rch_data = reformat_monthly_rch_file(rch_data_raw)

```



Activity 1:



